\documentclass{resume} % Use the custom resume.cls style

\usepackage{graphicx}
\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\newcommand{\PRLsep}{\noindent\makebox[\linewidth]{\resizebox{0.1\linewidth}{0.25pt}{$\bullet$}}}
\newcommand{\rExperience}[5]{
  \textbf{#1}, #2 \hfill #3

  #4
  
  \begin{center} \textsc{\scriptsize #5 } \end{center}
}


\name{Mark Dixon} % Your name
\address {
  +46 703 39 64 01 \\
  \href{mailto:mark@dixon.se}{mark@dixon.se} \\
  \href{https://linkedin.com/in/dixonse}{linkedin.com/in/dixon.se}
} 
\address {
}


\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{OBJECTIVE}

  %\iffalse{
    From building real-time physics engines to shaping climate tech
    policy—my career has been driven by curiosity across the full
    stack of technology and human systems. After helping scale
    ClimateView from idea to Series A as CTO, I'm now exploring how AI
    and open science can accelerate climate action as ClimateView's
    CSO.

    Ready to bring this systems-thinking approach to teams passionate
    about using technology as a force multiplier for positive change.
  %}\fi

  \iffalse{
    I thrive in the messy middle where complex technical challenges
    meet real-world impact. Whether it was creating haptic VR
    simulations, building learning platforms, or now architecting
    climate transition frameworks used by 230+ cities, I've spent 20+
    years making the technically possible practically useful.

    Seeking to join a team where deep technical craft, collaborative
    mentorship, and meaningful outcomes intersect.
  }\fi
  
\end{rSection}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

  {\bf Honours in Information Technology (Honours)}, Australian National University \hfill {1997}\\*
  First class honours.

  {\bf Bachelor of Information Technology}, Australian National University \hfill {1994 - 1996}

  {\bf Commerce (Information Systems)}, Curtin University \hfill {1993}

\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Mgmt & Start-ups, Product Management, Dev Management, C-level Management
\\*
Code & {\bf Python}, C/C++, Julia, C\#, TypeScript
\\*
Tech & Unix (Linux/BSD/IRIX), Windows, Django, Wagtail, TypeScript, LaTeX, Claude Code
\\*
Text & Emacs, org-mode, Jupyter/Marimo, Markdown, Zotero, Readwise Reader
\\*
GitHub & \href{https://github.com/nitwit-se}{https://github.com/nitwit-se}
\\*
\end{tabular}\\*
\end{rSection}


%----------------------------------------------------------------------------------------
% WORK EXPERIENCE
%----------------------------------------------------------------------------------------
\begin{rSection}{EXPERIENCE}

  {\rExperience
      {Chief Science Officer} {ClimateView AB} {May 2024 - present}
      {
        Worked initially as advisor / staff engineer during CTO hand-over period. Currently CSO responsible for research, prototyping, modelling and over-all scientific rigour of ClimateView and the Transition Element Framework (\href{https://transitionelements.org}{https://transitionelements.org} and \href{https://github.com/nitwit-se/transition-element-framework}{https://github.com/nitwit-se/transition-element-framework}).
      }
      {Climate Change Mitigation · Climate Action Planning · Data Science  \\*
        Large Language Models (LLM) · Model Context Protocol (MCP) · Julia · Python  · Marimo · Claude Code}
  }

  \PRLsep

  {\rExperience
    {IT Consultant / Owner} {Nitwit AB} {2017 - 2024}
    {Freelance consultant specialising in CTO (fractional or as-a-service) and advisory roles in startup companies.}
    {Business Strategy · Entrepreneurship · AI / Large Language Models (LLM) · Software Development}
  }

  \PRLsep

  {\rExperience
    {Fractional CTO} {ClimateView AB} {2018 - 2024}
    {As a hands-on CTO I took ClimateView AB from a 3-person startup to successful series-A round and subsequent recruitment of a full-time CTO.}
    {Python · Julia · C\# / .NET Core · TypeScript · DevOps · Data Science · Data Structures · Algorithms · Modeling}
  }

  \pagebreak
  \vspace*{1em}
  
  {\rExperience
    {Python Developer} {NextLVL Stockholm AB} {2017 - 2022}
    {As a consultant developer I built a modern Learning Managemnt System (LMS) written in Python/Django.}
    {Python · DevOps · AWS · EC2 / Elastic Beanstalk}
  }

  \PRLsep
  
  {\rExperience
    {Python Developer / Agile Coach} {Motivation Media Group AB} {2017 - 2018}
    {Consultant software developer and agile coach at Motivation.se, I developed the new \href{https://motivation.se}{Motivation.se 2.0} platform in Wagtail, a rewrite of the original PHP platform.}
    {Agile Methodologies · Python · Wagtail}
  }

  \PRLsep

  {\rExperience
    {Teacher} {Nackademin AB} {2017}
    {Internet of Things program at Nackademin, 3 courses (C/C++ programming, OOP and Algorithms \& Data Structures).}
    {Teaching · Data Structures · Algorithms · Object Oriented Programming}
  }

  \PRLsep

  {\rExperience
    {Product Manager} {Ping Pong AB} {2013 - 2017}
    {Initially a consultant scrum master, subsequently 1 year as development manager for 20 engineers and then 3 years as product manager. Ping Pong AB developed SaaS LMS tools for schools and universities in Sweden.}
    {Agile Methodologies · Scrum / Certified Scrum Master (CSM) · Learning Management Systems (LMS)}
  }

  \PRLsep

  {\rExperience
    {Software Engineer} {Research In Motion} {2012 - 2013}
    {Worked as consultant in a team of 9 developers based in Stockholm, developing the media applications for RIM's new BB10 OS.}
    {Python · Adobe Air · C++ · Qt · Cascade 4}
  }

  \PRLsep

  {\rExperience
    {Co-founder / CTO} {Nordic River AB} {2007 - 2012}
    {CTO responsible for devops, backend infrastructure and algorithms for docuemnt change analysis. Adobe Flash UI editor for visualising and merging changes; building desktop, web and iOS-based tools.}
    {Python · Adobe Flash/Flex/Air · ActionScript · C++ · Data Structures · Algorithms}
  }

  \PRLsep

  {\rExperience
    {Co-founder / CTO} {SenseGraphics AB} {2004 - 2007}
    {Worked on the design and development of H3D API, an open source 3D graphics library for development of stereoscopic VR applications (see \href{https://web.archive.org/web/20081217063248/http://www.h3dapi.org:80/}{www.h3dapi.org})}
    {Python · C/C++ · OpenGL · VRML/X3D · Open Source}
  }

  \pagebreak
  \vspace*{1em}

  {\rExperience
    {Software Engineer / CTO} {ReachIn Technologies AB} {1998 - 2004}
    {Developed and optimised a real-time physics library (C++) providing high performance (100Hz) 3D haptic simulation. Team lead for the core API team, subsequently CTO for the company during 2003-2004.}
    {Python · C/C++ · OpenGL · VRML · Haptics · Algorithms}
  }

  \PRLsep

  {\rExperience
    {Research Developer} {CSIRO Australia} {1998}
    {Research developer at the Australian CRC for Advanced Computational Systems (ACSys) and CSIRO in the Virtual Environments research group, developing SGI / Irix based VR applications.}
    {Python · C/C++ · OpenGL}
  }


\end{rSection} 


%----------------------------------------------------------------------------------------
%	Other Information
%----------------------------------------------------------------------------------------

\begin{rSection}{Recent Publications}
  \vspace{-1.25em}
\item \textbf{Designing for Delivery (2025)} {Co-authored a systems-based planning method (``Dual Lens of Transition Planning'') to help cities design and deliver fundable climate transition strategies, aligning ambition with investment-ready delivery through structured modelling, strategic interventions, and early indicators of progress.}

\item \textbf{Standardising Climate Mitigation: The Transition Element Framework (2024)} {Led development of the Transition Element Framework (TEF), a comprehensive methodology that transforms IPCC climate science into practical implementation tools, facilitating data-driven climate action planning for municipalities and regions globally. \href{https://www.transitionelements.org/downloads/white_paper_standardising_climate_mitigation.pdf}{Available here.}}
\item \textbf{Data-Driven Transitions: A co-created methodology (2024)} {Co-authored methodology white paper establishing a data-driven framework for climate transitions, integrating physics, behavioral science, and economics to help 230+ municipalities create actionable net-zero pathways through the ClimateView Platform. \href{https://www.transitionelements.org/downloads/white_paper_data_driven_transitions_2024_09_01.pdf}{Available here.}
}
\end{rSection} 


\begin{rSection}{Patents}
\begin{itemize}

\item \textbf{Computational modeling, climate plan scoring, and data tagging}
  {\href{https://patents.google.com/patent/US20230169231A1/en}{US20230169231A1}}

\item \textbf{Method and system for harmonization of variants of a sequential file}
  {\href{https://patents.google.com/patent/US8010507B2/en}{US8010507B2}}

\item \textbf{Method and system for facilitating the examination of documents}
  {\href{https://patents.google.com/patent/US8209605B2/en}{US8209605B2}}

%\item \textbf{Method and system for digital file flow management}
%  {\href{https://patents.google.com/patent/US20080177782A1/en}{US20080177782A1}}

%\item \textbf{Method and System for Access to Material on a Web Site}
%  {\href{https://patents.google.com/patent/US20090064284A1/en}{US20090064284A1}}

%\item \textbf{Method and system for distributed coordination of access to digital files}
%  {\href{https://patents.google.com/patent/US20090228716A1/en}{US20090228716A1}}

%\item \textbf{Method and system for invitational recruitment to a web site}
%  {\href{https://patents.google.com/patent/US20080208867A1/en}{US20080208867A1}}

\end{itemize}


\end{rSection} 


%----------------------------------------------------------------------------------------
\begin{rSection}{Extra-Curricular Activities} 
\begin{itemize}
  \item Running a small publishing house (Nitwit Förlag) on a hobby basis, working with typesetting, automation, and distribution; because it is creative, fun and... I love books.
\end{itemize}


\end{rSection}

%----------------------------------------------------------------------------------------
%\begin{rSection}{Heading} 
%\begin{itemize}
%    \item Text
%\end{itemize}
%\end{rSection}


\end{document}

